%-------------------------
% Resume in Latex
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
\usepackage{charter}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Kanishak Sharma} \\ \vspace{1pt}
    \small 7807330609 $|$ \href{https://mail.google.com/mail/?view=cm&fs=1&to=kanishak.sharma22@st.niituniversity.in&su=&body=}{kanishak.sharma22@st.niituniversity.in} $|$
    \href{https://www.linkedin.com/in/kanishak-xd}{LinkedIn [linkedin.com/in/kanishak-xd]} \\
    \href{https://github.com/Kanishak-xd}{GitHub [github.com/Kanishak-xd]} $|$
    \href{https://siegespace.vercel.app}{Portfolio [siegespace.vercel.app]}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Full Stack Developer Intern}{June 2025 -- July 2025}
    {Converge Digital}{Gurugram, Haryana}
  \resumeItemListStart
    \resumeItem{\textbf{\href{https://github.com/Kanishak-xd/auth-app}{github.com/Kanishak-xd/auth-app}}: Built a secure authentication system with login/signup, profile editing, role-based dashboards, and audit logging.}
    \resumeItem{\textbf{\href{https://github.com/Kanishak-xd/hrms-app}{github.com/Kanishak-xd/hrms-app}}: Developed a role-based HR management platform with dynamic dashboard, employee management, and master modules (Company, Department, etc.).}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
  \resumeSubheading
    {REJAP -- Language Learning Website -- \href{https://github.com/Kanishak-xd/rejap}{github.com/Kanishak-xd/rejap}}{June 2025 -- Present}
    {MongoDB Atlas, Express, React, Node.js, Firebase, TailwindCSS, Cloudinary}{}
    \resumeItemListStart
      \resumeItem{Built to help students prepare for the JLPT exam through interactive lessons, quizzes, progress tracking, and leaderboards.}
      \resumeItem{Developed responsive UI in Figma and TailwindCSS; implemented Firebase Auth, role-based control, and deployed on Vercel/Render.}
    \resumeItemListEnd

  \resumeSubheading
    {Threat Intelligence Dashboard -- \href{https://github.com/Kanishak-xd/threat-intel}{github.com/Kanishak-xd/threat-intel}}{Jan 2025 -- May 2025}
    {MongoDB Atlas, Express, React, Node.js, Docker, Jenkins, AWS EC2}{}
    \resumeItemListStart
      \resumeItem{Built in a team of 4 to collect and visualize honeypot data, showing attack patterns, credentials, and geolocation insights.}
      \resumeItem{Designed and integrated backend APIs; deployed honeypot on AWS EC2, backend on Render, and frontend on Netlify.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%----------EDUCATION----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {NIIT University}{Neemrana, Rajasthan}
      {Bachelor of Technology in Computer Science and Engineering}{2022 -- 2026}
    \resumeItemListStart
      \resumeItem{\textbf{Relevant Modules:} Object-Oriented Programming, Software Engineering, Capstone I \& II, Design Thinking and Interactive Technologies, Cloud Computing Concepts, Database Management Systems, Data Structures, Fundamentals of Computer Programming, Japanese Language – Levels 1, 2 \& 3}
    \resumeItemListEnd

    \resumeSubheading
      {D.A.V Sr. Sec. Public School (CBSE)}{Kangra, Himachal Pradesh}
      {XII}{2022}

    \resumeSubheading
      {D.A.V Public School (CBSE)}{Hamirpur, Himachal Pradesh}
      {X}{2020}
\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{
    \item{
      HTML, CSS, JavaScript, MongoDB, Express, React, Node, Angular, TailwindCSS, Bootstrap, Firebase, JWT, Git, Docker, VirtualBox, Jenkins, Vercel, Netlify, Render, Jira, Asana, Notion, Figma, Photoshop, Canva, Japanese language (JLPT N5 Certified) 
    }
  }
\end{itemize}

%-----------POSITIONS OF RESPONSIBILITY-----------
\section{Positions of Responsibility}
\resumeSubHeadingListStart
  \resumeSubheading
    {Coordinator – Consilio, The Design Club}{Jan 2024 -- Dec 2024}
    {NIIT University}{Neemrana, Rajasthan}
  \resumeItemListStart
    \resumeItem{Organized and led design workshops on Photoshop, Canva, and core design principles.}
    \resumeItem{Collaborated with Sinusoid Fest to host a web development competition and curated campus exhibitions showcasing top student designs.}
  \resumeItemListEnd

  \resumeSubheading
    {Member – Student Affairs Committee (SAC)}{Jan 2024 -- Dec 2024}
    {NIIT University}{Neemrana, Rajasthan}
  \resumeItemListStart
    \resumeItem{Designed official student ID cards and branding assets for university initiatives.}
    \resumeItem{Collaborated on events to address student concerns and enhance campus life.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
